---
title: "Ghana_2019_AndyNolan"
author: "Andy Kim and Nolan Gunter"
date: "today's date"
output: pdf_document
---

First, read in (and install if necessary) the libraries

```{r read libraries}
library(devtools)
library(EconomicClusters) #devtools::install_github("Lauren-Eyler/EconomicClusters")
library(haven)
library(weights)
library(parallelDist) #install.packages('parallelDist')
library(foreach)
library(doParallel)
library(survey)
library(Hmisc)
library(descr) #install.packages('descr')
library(tidyverse)
library(car)
library(stats)
```

If you have Dropbox synced to your computer files, then running the following code chunk should be sufficient to read in the data. Modify if necessary.

```{r read data}
dataset <- read_dta("~/Dropbox/EconomicClusters/andy&nolan/Ghana/GHHR82DT/GHHR82FL.DTA")
#individual <-read_dta("~/Dropbox/EconomicClusters/Ethiopia_2016/ETIR70DT/ETIR70FL.DTA")
```

Next, we use the information from the DHS Wealth Index PCA data from: https://dhsprogram.com/topics/wealth-index/Wealth-Index-Construction.cfm

For this analysis, the cutoff value we chose to subset the data was 0.05. Other cutoff points are valid.

Pages 2-4 of this document detail how this PCA was run: https://dhsprogram.com/programming/wealth%20index/Steps_to_constructing_the_new_DHS_Wealth_Index.pdf

```{r}
pca <- readxl::read_xlsx("~/Dropbox/EconomicClusters/andy&nolan/Ghana/ghana 2019 pca.xlsx")
imp_pca <- pca %>% filter(PCA >= 0.03)
```

```{r}
dataset <- dataset %>% 
  mutate(setting=car::recode(as.numeric(hv025),
                          "1 = 'urban';
                          2 = 'rural';
                          else = NA",
                          as.factor = TRUE,
                          levels = c('urban', 'rural')),
         water=car::recode(as.numeric(hv201),
                          "11 = 'pipe_dwel';
                          12 = 'pipe_yard'; 
                          13 = 'pipe_neighbor'; 
                          14 = 'pipe_public'; 
                          c('20','21','30','31','32') = 'well';
                          c('41', '42', '43', '51') = 'surface';
                          c('61', '62', '71', '96') = 'other';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('pipe_dwel', 'pipe_yard', 'pipe_neighbor', 
                                   'pipe_public', 'well', 'surface', 'other')),
         toilet=car::recode(as.numeric(hv205),
                          "c('10','11','12','13','14','15') = 'flush';
                          c('20', '21', '22', '23') = 'pitlat';
                          c('41', '42', '43', '96') = 'other';
                          31 = 'none';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('flush', 'pitlat', 'none', 'other')),
         cookfuel=car::recode(as.numeric(hv226),
                          "1 = 'electricity';
                          2 = 'LPG'; 
                          3 = 'natural gas'; 
                          4 = 'biogas'; 
                          5 = 'kerosene';
                          6 = 'coal/lignite'; 
                          7 = 'charcoal'; 
                          8 = 'wood'; 
                          9 = 'straw/shrubs/grass'; 
                          10 = 'crop';
                          11 = 'dung'; 
                          95 = 'nofoodcookedinhouse'; 
                          96 = 'other';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('electricity', 'LPG', 'natural gas', 
                                   'biogas', 'kerosene', 'coal/lignite', 'charcoal',
                                   'wood', 'straw/shrubs/grass', 'crop', 'dung',
                                   'nofoodcookedinhouse', 'other')),
         floor=car::recode(as.numeric(hv213),
                          "c('11','12') = 'natural';
                          c('21', '22') = 'rudimentary';
                          c('31', '32', '33', '34', '35') = 'finished';
                          96 = 'other';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('natural', 'rudimentary', 'finished', 'other')),
         roof=car::recode(as.numeric(hv215),
                          "c('11','12', '13') = 'natural';
                          c('21', '22', '23', '24') = 'rudimentary';
                          c('31', '32', '33', '34', '35', '36') = 'finished';
                          96 = 'other';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('natural', 'rudimentary', 'finished', 'other')),
         wall=car::recode(as.numeric(hv214),
                          "c('11','12', '13') = 'natural';
                          c('21', '22', '23', '24', '25', '26') = 'rudimentary';
                          c('31', '32', '33', '34', '35', '36') = 'finished';
                          96 = 'other';
                          else = NA",
                          as.factor=TRUE,
                          levels=c('natural', 'rudimentary', 'finished', 'other')),)
```


```{r}
data_full <- dataset %>% select(water, toilet, cookfuel, hv206, hv207, hv208, hv209, hv212, hv213, hv214, hv243a, hv243b, hv243e, hv247, sh114g, sh114i, sh114k, sh114m, sh114n, sh114o, sh114p)

colnames(data_full)<-c("water", "toilet", "cooking fuel", "electricity", "radio", "television","refrigerator", "cartruck", "floor", "wall", "cell", "watch", "computer", "bankaccount", "freezer", "washingmachine", "dvd", "bed", "table", "chair", "cabinet")
                       
## how exactly should we define an asset? For this example, it seems that all of the important variables ARE assets. 

assets <- dataset %>% select(water, toilet, cookfuel, hv206, hv207, hv208, hv209, hv212, hv213, hv214, hv243a, hv243b, hv243e, hv247, sh114g, sh114i, sh114k, sh114m, sh114n, sh114o, sh114p)

colnames(assets)<-c("water", "toilet", "cooking fuel", "electricity", "radio", "television","refrigerator", "cartruck", "floor", "wall", "cell", "watch", "computer", "bankaccount", "freezer", "washingmachine", "dvd", "bed", "table", "chair", "cabinet")

#assets <- dataset %>% select(hv208, hv206, water, hv209, sh121j, sh121i, hv247, cookfuel, roof, hv243a, sh121g, toilet, floor, hv244)

#colnames(assets)<-c("TV", "electricity", "water", "refrigerator", "mitad", "bed", "bank", "cooking fuel", "roof", "cell", "table", "toilet", "floor", "agland")
dejure<-dataset$hv012
defacto<-dataset$hv013
hhwt<-dataset$hv005

data_for_EC<-EC_DHSwts(assets, dejure, defacto, hhwt)
```

```{r}
numCores <- detectCores()
doParallel::registerDoParallel(cores=numCores)

if (class(data_for_EC[,1])=="numeric"){
  wt<-data_for_EC[,1]
  data_for_EC<-data_for_EC[,-1]
} else {
  wt<-rep(1, nrow(data_for_EC))
}

col_cat<-seq_len(ncol(data_for_EC))

# Create all possible combinations of 4
combn<-utils::combn(c(1:ncol(data_for_EC)),4)

col_indx=matrix(c("NULL"), ncol(combn), ncol(data_for_EC), byrow=FALSE)
for (i in 1:ncol(combn)){
  col_indx[i,]<-t(is.element(col_cat, combn[,i]))
  col_indx[i,][col_indx[i,]==FALSE]<-NA
  colnames(col_indx)=colnames(data_for_EC)
}

ASW<-vector()
combi<-list()
parD<-list()
wcKMR<-list()
start.time<-Sys.time()
# switch to i=1:nrow(col_indx) when you're ready
ASW<-foreach::foreach (i=1:nrow(col_indx), .combine='c')  %dopar% {
  combi<-data_for_EC[,!is.na(col_indx[i,])]
  combi_mat<-data.matrix(combi)
  print(names(combi))
  parD<-parDist(combi_mat, method =  "hamming") 
  wcKMR<-WeightedCluster::wcKMedRange(parD, kvals=(5), weights=wt)
  ASW[i]<-wcKMR$stats[,5]
  rm(combi)
  rm(parD)
  rm(wcKMR)
  return(ASW[i])
}
end.time<-Sys.time()
total<-end.time-start.time

ASW_max<-max(ASW, na.rm=TRUE)
ASW_maxind <- which(ASW==ASW_max)

combi_maxASW<- data.matrix(data_for_EC[,!is.na(col_indx[ASW_maxind,])])

parD<-parDist(combi_maxASW, method = "hamming", threads = numCores) 
wcKMR<-WeightedCluster::wcKMedRange(parD, kvals=5, weights=wt)
```

The cluster with the largest ASW is: car/truck, cell, computer, and washing machine. 

```{r}
#hv005 = household sample weight
dataset$weights<-dataset$hv005/1000000
dataset$cluster<- c()

dataset <- dataset %>% 
  mutate(cluster=car::recode(unlist(wcKMR$clustering),
                          "16514 = 1;
                          16625 = 2;
                          16645 = 3;
                          16097 = 4;
                          16495 = 5"))

col_cat<-seq_len(ncol(data_for_EC))
```

```{r}
svydesign<-svydesign(dataset$hv001, weights=dataset$weights,  strata=dataset$hv022, data=dataset)

svytable(~dataset$cluster, design=svydesign)/nrow(dataset)
#         1          2          3          4      5
#0.11897460 0.03899174 0.07539326 0.04932219  0.71731821
```

```{r}
HAZ_av<-matrix(nrow=nrow(dataset), ncol=6)

## why are we doing hc70_1?
## need to understand this better??

HAZ_av[,1]<-dataset$hc70_1
HAZ_av[,2]<-dataset$hc70_2
HAZ_av[,3]<-dataset$hc70_3
HAZ_av[,4]<-dataset$hc70_4
HAZ_av[,5]<-dataset$hc70_5
HAZ_av[,6]<-dataset$hc70_6
for (i in 1:nrow(HAZ_av)){
  for (j in 1:6){
    if(is.na(HAZ_av[i,j])==TRUE | HAZ_av[i,j]==9999 | HAZ_av[i,j]==9998 | HAZ_av[i,j]==9996 | HAZ_av[i,j]==9997){
      HAZ_av[i,j]<-NA}
  }
}

dataset$HAZ_av<-NULL
for (i in 1:nrow(dataset)){
  dataset$HAZ_av[i]<-mean(HAZ_av[i,], na.rm=TRUE)
  if(dataset$HAZ_av[i]=="NaN"){
    dataset$HAZ_av[i]<-NA
  }
}

dataset$HAZ_av<-dataset$HAZ_av/100

summary(dataset$HAZ_av)
#9816 NAs, so HAZ available for kids from 6834 households
```

```{r}
dataset$weights<-dataset$hv005/1000000

svydesign_HAZ<-svydesign(dataset$hv001, weights=dataset$weights,  strata=dataset$hv022, data=dataset)
options(survey.lonely.psu="remove")


C1<-subset(dataset, dataset$cluster==1)
C1_design<-subset(svydesign_HAZ, dataset$cluster==1)
C1_HAZsvy<-svymean(C1$HAZ_av, C1_design, na.rm=TRUE)
HAZ_av_mean_C1_wtd<-mean(C1_HAZsvy)
HAZ_sem_C1<-SE(C1_HAZsvy)

C2<-subset(dataset, dataset$cluster==2)
C2_design<-subset(svydesign_HAZ, dataset$cluster==2)
C2_HAZsvy<-svymean(C2$HAZ_av, C2_design, na.rm=TRUE)
HAZ_av_mean_C2_wtd<-mean(C2_HAZsvy)
HAZ_sem_C2<-SE(C2_HAZsvy)

C3<-subset(dataset, dataset$cluster==3)
C3_design<-subset(svydesign_HAZ, dataset$cluster==3)
C3_HAZsvy<-svymean(C3$HAZ_av, C3_design, na.rm=TRUE)
HAZ_av_mean_C3_wtd<-mean(C3_HAZsvy)
HAZ_sem_C3<-SE(C3_HAZsvy)

C4<-subset(dataset, dataset$cluster==4)
C4_design<-subset(svydesign_HAZ, dataset$cluster==4)
C4_HAZsvy<-svymean(C4$HAZ_av, C4_design, na.rm=TRUE)
HAZ_av_mean_C4_wtd<-mean(C4_HAZsvy)
HAZ_sem_C4<-SE(C4_HAZsvy)

C5<-subset(dataset, dataset$cluster==5)
C5_design<-subset(svydesign_HAZ, dataset$cluster==5)
C5_HAZsvy<-svymean(C5$HAZ_av, C5_design, na.rm=TRUE)
HAZ_av_mean_C5_wtd<-mean(C5_HAZsvy)
HAZ_sem_C5<-SE(C5_HAZsvy)

HAZ_av_mean<-rbind(HAZ_av_mean_C1_wtd, HAZ_av_mean_C2_wtd, HAZ_av_mean_C3_wtd, HAZ_av_mean_C4_wtd, HAZ_av_mean_C5_wtd)
HAZ_sem<-rbind(HAZ_sem_C1, HAZ_sem_C2, HAZ_sem_C3, HAZ_sem_C4, HAZ_sem_C5)

HAZ_df<-data.frame(
  x=c(1:5),
  y=HAZ_av_mean,
  sem=HAZ_sem
)
```

NOTE: this code chunk particulary the FOR loops are very slow, way to improve efficiency?

```{r}
plot(HAZ_av_mean, xlab="Economic Groups", ylab="Average Child Height-for-Age Z-Score", main="Mean Child Height-for-Age Z-Score by Combined Economic Group", ylim=c(-1.8,0))
with(
  data=HAZ_df,
  expr= errbar(x, y, y+sem, y-sem, add=T, pch=1, cap=0.015)
)
```

